---
title: "Assignment 3"
author: "Jill Hunt"
date: '2018-03-14'
output: html_document
---

## Creating dataset of 2 types of roads (Smooth and Bumpy), with 20 roads of each type sampled

```{r}

n.groups <- 2
n.sample <- 20
n <- n.groups * n.sample

x <- rep(1:n.groups, rep(n.sample, n.groups))
road.type <- factor(x, labels = c("Smooth", "Bumpy"))
acci <- runif(n, 1, 30) #There are no less than 1 and no more than 30 accidents per road sampled
accid <- acci - mean(acci)

```

## Designing a matrix for the interaction between road type and accidents
15 = expected accidents on smooth road
5 = difference between expected accidents on smooth road and bumpy road
3 = slope 
1 = difference in slope between bumpy and smooth
```{r}

Xmat <- model.matrix(~road.type*accid)
beta.vec <- c(15, 5, 3, 1)

```

## Assemble into a poisson model
```{r}

lin.pred <- Xmat[,] %*% beta.vec
lambda <- exp(lin.pred)
C <- rpois(n = n, lambda = lambda)

```

Now assess the model
```{r}

mod1 <- glm(C ~ road.type * accid, poisson)
summary(mod1)

```
```{r}

par(mfrow = c(2, 2))
plot(mod1)

```

